Report

### 2021-05-28 Rmd/report.Rmd
Fix bug in line 583

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
y_pred <- logit_to_prob(predict(fit))
sample_size <- participants %>% 
	filter(valid_participant) %>%
	count(age_group, lp)

gaze %>% 
	drop_na() %>% 
	ggplot(aes(x = ot1, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, aes(y = y_pred), geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, aes(y = y_pred), geom = "line", size = 1) +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

>>>>

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant) %>%
	count(age_group, lp)

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```
